Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-09 examples.tex
+

@@

;; Ensure there's a place to put the L1 mapping
mov %rdi, %r13

@@

@@

@@

@@

@@

\caption{Distilled code for mapping a new page}

@@

\begin{figure}
\begin{lstlisting}
;; Assume the save-space is in rdi,
;; load-space in rsi
;; No need to save/restore caller-save regs
;; Save yielding context
mov 0[%rdi], %rbx
mov 8[%rdi], %rsp
mov 16[%rdi], %rbp
mov 24[%rdi], %r12
mov 32[%rdi], %r13
mov 40[%rdi], %r14
mov 48[%rdi], %r15
mov 56[%rdi], %cr3
;; Restore target context
mov %rbx, 0[%rsi] 
;; This switches to a new stack
;; This stack may not be mapped in the
;; current address space!
mov %rsp, 8[%rsi] 
mov %rbp, 16[%rsi]
mov %r12, 24[%rsi]
mov %r13, 32[%rsi]
mov %r14, 40[%rsi]
mov %r15, 48[%rsi]
;; Switch to the new address space
mov %cr3, 56[%rsi]
\end{lstlisting}
\caption{Basic task switch code that switches address spaces.}
\label{fig:swtch}
\end{figure}

>>>>

%\begin{figure*}\small
%\[
%\proofoutstep{x:\isolated\;\texttt{Node},y:\INT,z:\bool}
%{
 %   \proofoutstep{x:\isolated\;\texttt{Node},y:\INT,z:\bool}
  %  {
   %     \proofoutstep{x:\writable\;\texttt{Node},y:\INT,z:\bool}
    %    {
     %       \proofoutstep{x:\writable\;\texttt{Node},y:\INT,z:\bool}
      %      {
       %       mov\texttt{ }rdi \; r13
        %    }{\textsc{T-Alloc}}
         %   {x:\writable\;\texttt{Node},y:\writable\;\texttt{Node},z:\bool}\\
          %  \;\;\;z\texttt{=}x\texttt{.next;}\\
           % \specline{x:\writable\;\texttt{Node},y:\writable\;\texttt{Node},z:\writable\;\texttt{Node}}\\
            %\;\;\;y\texttt{.next=}z\texttt{;}\\
            %\specline{x:\writable\;\texttt{Node},y:\writable\;\texttt{Node},z:\writable\;\texttt{Node}}\\
            %\;\;\;z\texttt{.prev=}y\texttt{;}\\
            %\specline{x:\writable\;\texttt{Node},y:\writable\;\texttt{Node},z:\writable\;\texttt{Node}}\\
            %\;\;\;y\texttt{.prev=}x\texttt{;}\\
         %\specline{x:\writable\;\texttt{Node},y:\writable\;\texttt{Node},z:\writable\;\texttt{Node}}\\
          %  \;\;\;x\texttt{.next=}y\texttt{;}\\
         %\specline{x:\writable\;\texttt{Node},y:\writable\;\texttt{Node},z:\writable\;\texttt{Node}}
        %}
        %{\textsc{T-Seq}*~\textrm{across}~\textsc{T-FieldRead}\\\textrm{and}~\textsc{T-FieldWrite}}
        %{x:\writable\;\texttt{Node},y:\writable\;\texttt{Node},z:\writable\;\texttt{Node}}
    %}
    %{\textsc{T-SubEnv}}
    %{x:\writable\;\texttt{Node}}
%}
%{\textsc{T-RecovIso}}
%{x:\isolated\;\texttt{Node}}
%\]
%\caption{Typing derivation for adding a node to an isolated doubly-linked list.}
%\label{fig:recoviso_example}
%\end{figure*}
\lstset{
  columns=fullflexible,
  numbers=left,
  basicstyle=\ttfamily,
  keywordstyle=\color{blue}\bfseries,
  morekeywords={mov,add,call},
  emph={rsp,rdx,rax,rbx,rbp,rsi,rdi,rcx,r8,r9,r10,r11,r12,r13,r14,r15},
  emphstyle=\color{green},
  emph={[2]cr3},
  emphstyle={[2]\color{violet}},
  morecomment=[l]{;;}
\newcommand{\fpaddr}{\texttt{fpaddr}}

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred,\rtv)  \ast  \texttt{r14}\mapsto_{r} \_ \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \_ \ast \ulcorner \texttt{aligned va} \land  \theta \; !!\; \texttt{maddr} = \texttt{None}\urcorner}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred,\rtv) \ast  \texttt{r14}\mapsto_{r} \_ \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \_ \ast }$
$\specline{\exists (\entryf ,\;\entrytr,\; \entrytw,\; \entryo: \texttt{word 64}) \ldotp \ulcorner (\texttt{addr\_L1 }\vaddr) = \entryo\urcorner \ast }$
$\specline{\nfpointsto{\mask\vaddr\ft\rtv}{\mask\vaddr\tw\rtv}\entryf\qone\naddr \ast}$ 
$\specline{  \nfpointsto{\mask\vaddr\ft\entryf}{\mask\vaddr\tw\entryf}\entrytr\qtwo\naddr \ast \nfpointsto{\mask\vaddr\ft\entrytr}{\mask\vaddr\tw\entrytr}\entrytw\qthree\naddr \ast}$
$\specline{\texttt{pte\_addr} \mapsto_{\texttt{vpte},\rtv} \entryo \;(\texttt{wzero 64}) \ast \texttt{rax}\mapsto_{r} \texttt{pte\_addr}  }$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred,\rtv) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \_ \ast }$
$\specline{ \nfpointsto{\mask\vaddr\ft\rtv}{\mask\vaddr\tw\rtv}\entryf\qone\naddr \ast}$ 
$\specline{  \nfpointsto{\mask\vaddr\ft\entryf}{\mask\vaddr\tw\entryf}\entrytr\qtwo\naddr \ast \nfpointsto{\mask\vaddr\ft\entrytr}{\mask\vaddr\tw\entrytr}\entrytw\qthree\naddr \ast}$
$\specline{\texttt{pte\_addr} \mapsto_{\texttt{vpte},\rtv} \entryo \;(\texttt{wzero 64}) \ast \texttt{rax}\mapsto_{r} \texttt{pte\_addr}  }$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred,\rtv) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \_ \ast}$
$\specline{ \nfpointsto{\mask\vaddr\ft\rtv}{\mask\vaddr\tw\rtv}\entryf\qone\naddr \ast}$ 
$\specline{  \nfpointsto{\mask\vaddr\ft\entryf}{\mask\vaddr\tw\entryf}\entrytr\qtwo\naddr \ast \nfpointsto{\mask\vaddr\ft\entrytr}{\mask\vaddr\tw\entrytr}\entrytw\qthree\naddr \ast}$
$\specline{\texttt{pte\_addr} \mapsto_{\texttt{vpte},\rtv} \entryo \;(\texttt{wzero 64}) \ast \texttt{rax}\mapsto_{r} \texttt{pte\_addr}  }$
$\specline{\exists \texttt{ fpaddr} \ldotp \ulcorner \texttt{aligned fpaddr} \urcorner \ast \texttt{rax}\mapsto_{r} \texttt{fpaddr} \ast \texttt{fpaddr} \mapsto_{a} (\texttt{wzero 64})}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred,\rtv) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \_ \ast}$
$\specline{\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\vaddr,\rtv,\entryf,\entrytr,\entrytw,\entryo) \ast \ulcorner \theta \;!!\; \texttt{maddr} = \texttt{None}\urcorner}$
$\specline{\ulcorner \texttt{aligned fpaddr} \urcorner \ast \texttt{rax}\mapsto_{r} \texttt{fpaddr} \ast \texttt{fpaddr} \mapsto_{a} (\texttt{wzero 64})}$
$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \sqsubseteq $
$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta<[\vaddr:=\texttt{fpaddr}]>),\gammaPred,\rtv) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \_ }$
$\specline{\ulcorner \texttt{aligned fpaddr} \urcorner \ast \texttt{rax}\mapsto_{r} \texttt{fpaddr} \ast \texttt{aligned va} \ast\sumwalkabs\vaddr\qfrac\fpaddr}$

@@

\caption{Specification and proof of distilled code for mapping a new page with $\textsf{wpd\_def }_{\rtv}$}

@@

\begin{figure}
\begin{lstlisting}
;; Assume the save-space is in rdi,
;; load-space in rsi
;; No need to save/restore caller-save regs
;; Save yielding context
$\specline{}$  
mov 0[%rdi], %rbx
mov 8[%rdi], %rsp
mov 16[%rdi], %rbp
mov 24[%rdi], %r12
mov 32[%rdi], %r13
mov 40[%rdi], %r14
mov 48[%rdi], %r15
mov 56[%rdi], %cr3
;; Restore target context
mov %rbx, 0[%rsi] 
;; This switches to a new stack
;; This stack may not be mapped in the
;; current address space!
mov %rsp, 8[%rsi] 
mov %rbp, 16[%rsi]
mov %r12, 24[%rsi]
mov %r13, 32[%rsi]
mov %r14, 40[%rsi]
mov %r15, 48[%rsi]
;; Switch to the new address space
mov %cr3, 56[%rsi]
\end{lstlisting}
\caption{Basic task switch code that switches address spaces.}
\label{fig:swtch}
\end{figure}
